% (c) 2002 Matthew Boedicker <mboedick@mboedick.org> (original author) http://mboedick.org
% (c) 2003-2007 David J. Grant <davidgrant-at-gmail.com> http://www.davidgrant.ca
% (c) 2008 Nathaniel Johnston <nathaniel@nathanieljohnston.com> http://www.nathanieljohnston.com
%
%This work is licensed under the Creative Commons Attribution-Noncommercial-Share Alike 2.5 License. To view a copy of this license, visit http://creativecommons.org/licenses/by-nc-sa/2.5/ or send a letter to Creative Commons, 543 Howard Street, 5th Floor, San Francisco, California, 94105, USA.

\documentclass[letterpaper,11pt]{article}
\newlength{\outerbordwidth}
\pagestyle{empty}
\raggedbottom
\raggedright
\usepackage[svgnames]{xcolor}
\usepackage{framed}
\usepackage{tocloft}
\usepackage{url}
\usepackage{array}

%-----------------------------------------------------------
%Edit these values as you see fit

\setlength{\outerbordwidth}{3pt}  % Width of border outside of title bars
\definecolor{shadecolor}{gray}{0.75}  % Outer background color of title bars (0 = black, 1 = white)
\definecolor{shadecolorB}{gray}{0.93}  % Inner background color of title bars


%-----------------------------------------------------------
%Margin setup

\setlength{\evensidemargin}{-0.25in}
\setlength{\headheight}{0in}
\setlength{\headsep}{0in}
\setlength{\oddsidemargin}{-0.25in}
\setlength{\paperheight}{11in}
\setlength{\paperwidth}{8.5in}
\setlength{\tabcolsep}{0in}
\setlength{\textheight}{9.5in}
\setlength{\textwidth}{7in}
\setlength{\topmargin}{-0.3in}
\setlength{\topskip}{0in}
\setlength{\voffset}{0.1in}


%-----------------------------------------------------------
%Custom commands
\newcommand{\resitem}[1]{\item #1 \vspace{-2pt}}
\newcommand{\resheading}[1]{\vspace{8pt}
  \parbox{\textwidth}{\setlength{\FrameSep}{\outerbordwidth}
    \begin{shaded}
\setlength{\fboxsep}{0pt}\framebox[\textwidth][l]{\setlength{\fboxsep}{4pt}\fcolorbox{shadecolorB}{shadecolorB}{\textbf{\sffamily{\mbox{~}\makebox[6.762in][l]{\large #1} \vphantom{p\^{E}}}}}}
    \end{shaded}
  }\vspace{-5pt}
}
\newcommand{\ressubheading}[4]{
\begin{tabular*}{6.5in}{l@{\cftdotfill{\cftsecdotsep}\extracolsep{\fill}}r}
		\textbf{#1} & #2 \\
		\textit{#3} & \textit{#4} \\
\end{tabular*}\vspace{-6pt}}
%-----------------------------------------------------------

% Remove the bullet points.
\renewcommand{\labelitemi}{}

\begin{document}

\begin{tabular*}{7in}{l@{\extracolsep{\fill}}r}
\textbf{\Large John A. Ramey II, Ph.D.} &  \\
Data Scientist, BlackLocus: Home Depot Innovation Lab & johnramey@gmail.com \\
Austin, Texas, USA & http://ramhiser.com \\
\end{tabular*}
\\

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\resheading{Personal Statement}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
  \begin{center}
  \parbox{6.762in}{I build intelligent systems in the form of data products that utilize data to inform human users to make better decisions and to automate processes that require extensive time, labor, and resources. My research interests are in statistical and machine learning with an emphasis on Bayesian methods.}
  \end{center}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\resheading{Education}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{itemize}
\item
	\ressubheading{Baylor University}{Waco, TX}{Ph.D. Statistics}{July 2012}
	\begin{itemize}
		\resitem{Adviser: Dean M. Young, Ph.D.}
	\end{itemize}
\item
	\ressubheading{Baylor University}{Waco, TX}{M.Sc. Statistics}{Dec. 2009}
\item
	\ressubheading{Baylor University}{Waco, TX}{B.Sc. Mathematics (Minor: Computer Science)}{Aug. 2008}
\end{itemize}
  
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\resheading{Publications}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{itemize}
	\resitem{Finak, G., Frelinger J., Jiang, W., Newell, E., \textbf{Ramey, J.}, Davis, M., Kalams, S., de Rosa, S., and Gottardo, R. (2014) ``OpenCyto: An Open Source Infrastructure for Scalable, Robust, Reproducible, and Automated, End-to-End Flow Cytometry Data Analysis,'' \emph{PLOS Computational Biology}, 10, 8.}
	\resitem{\textbf{Ramey, J. A.} and Young, P. D. (2013) ``A Comparison of Regularization Methods Applied to the Linear Discriminant Function with High-Dimensional Microarray Data,'' \emph{Journal of Statistical Computation and Simulation}, 83, 3, 581--596.}
	\resitem{McDermott, J., Wang, J., Mitchell, H., Webb-Robertson, B., Hafen, R., \textbf{Ramey, J.}, and Rodland, K. (2013) ``Challenges in Biomarker Discovery: Combining Expert Insights with Statistical Analysis of Complex Omics Data,'' \emph{Expert Opinion on Medical Diagnostics}, 7, 1, 37--51.}
\end{itemize}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\resheading{Articles Submitted for Publication}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{itemize}
%	\resitem{\textbf{Ramey, J. A.}, Stein, C. K., and Young, D. M., ``High-Dimensional Regularized Discriminant Analysis.''}
%	\resitem{\textbf{Ramey, J. A.}, Sego, L. H., and Young, D. M. ``Cluster Stability Evaluation via Cluster Omission.'' (under revision)}
	\resitem{Sego, L. H., Shulman, S. A., Anderson, K. K., \textbf{Ramey, J. A.}, Wilson, J. E., Pulsipher, B. A., and Sieber, W. K. ``A Bayesian Acceptance Sampling Model for Combining Judgmental and Randomly Selected Samples.'' (under revision)}
\end{itemize}

\clearpage

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\resheading{Software Projects (Available at http://github.com/ramhiser)}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{itemize}
	\resitem{{\tt activelearning}: An R Package for Querying Unlabeled Observations with Active Learning.}
	\resitem{{\tt clusteval}: Evaluation of Clustering Algorithms in R.}
	\resitem{{\tt datamicroarray}: Collection of High-Dimensional Microarray Data Sets.}
	\resitem{{\tt itertools2}: A port of Python's {\tt itertools} module to R for efficient looping via iterators.}
	\resitem{{\tt noncensus}: An R collection to interface with data collected by the U.S. Census Bureau.}
	\resitem{{\tt openCyto}: An R Package for Automated Analysis of Flow Cytometry Data.}
	\resitem{{\tt sortinghat}: An R package for error-rate estimation methods for supervised classification.}
	\resitem{{\tt sparsediscrim}: An R Package for Regularized and Sparse Discriminant Analysis Methods.}
\end{itemize}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\resheading{Research Experience}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{itemize}
	\item 
	\ressubheading{Fred Hutchinson Cancer Research Center}{Seattle, WA}{Postdoctoral Research Fellow}{August 2012-October 2013}
	\item 
	\ressubheading{Pacific Northwest National Laboratory}{Richland, WA}{Research Associate, National Security Internship Program}{June 2011 - July 2012}
	\item
		\ressubheading{Statistical and Machine Learning Research Group}{Waco, TX}{Department of Statistical Science, Baylor University}{2009-2012}
	\item
		\ressubheading{Research Experience for Undergraduates at The Ohio State University}{Columbus, OH}{Vertical Integration of Research and Education in Computational Mathematics}{Summer 2004}
\end{itemize}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\resheading{Conference Papers}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{itemize}
	\resitem{\textbf{Ramey, J. A.} and Young, D. M. (2010). \textit{A More Computationally Efficient Model Selection Method for Regularized Discriminant Analysis}, Joint Statistical Meetings Proceedings, Vancouver, BC, Canada.}
\end{itemize}

 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\resheading{Awards, Grants \& Honors}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
	\vspace{-2pt}
	\begin{center}\begin{tabular*}{6.6in}{l@{\extracolsep{\fill}}r}
		\multicolumn{2}{c}{Travel Grant, \$1,000 -- Baylor University\cftdotfill{\cftdotsep}2011}\\	
		\multicolumn{2}{c}{Outstanding Graduate Student -- Department of Statistical Science, Baylor University\cftdotfill{\cftdotsep}2011}\\
		\multicolumn{2}{c}{JSM Stat Bowl -- Champion\cftdotfill{\cftdotsep} 2010}\\
		\multicolumn{2}{c}{Outstanding First Year Graduate Student -- Department of Statistical Science\cftdotfill{\cftdotsep}2009}\\
		\multicolumn{2}{c}{Baylor University Dean's Scholarship \cftdotfill{\cftdotsep} 2008-2012}\\
		\vphantom{E}
\end{tabular*}
\end{center}\vspace*{-16pt}

\clearpage

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\resheading{Invited Talks}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{itemize}
	\resitem{\textbf{Ramey, J. A.} (November 2012). \emph{Automated Bayesian Gating with OpenCyto}. FlowCAP-III Summit, National Institute of Health, Bethesda, Maryland, USA.}
	\resitem{\textbf{Ramey, J. A.} (February 2012). \emph{Diagonal Discriminant Analysis with Simultaneous Diagonalization of Covariance Matrices}. Fred Hutchison Cancer Research Center, Seattle, Washington, USA.}
	\resitem{\textbf{Ramey, J. A.} (February 2011). \emph{Diagonal Discriminant Analysis after Simultaneous Diagonalization of Covariance Matrices with High-Dimensional Data}. Pacific Northwest National Laboratory, Richland, Washington, USA.}
\end{itemize}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\resheading{Presentations}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{itemize}
	\resitem{\textbf{Ramey, J.}, Stein, C. K., and Young, D. M. (June 2013) \emph{High-Dimensional Regularized Discriminant Analysis}. Southern Regional Council on Statistics 2013, Louisville, Kentucky, USA. (poster)} 
	\resitem{\textbf{Ramey, J.}, Finak, G., Jiang, M., Taghiyar, J., de Rosa, S., Brinkman, R., and Gottardo, R.\ \  \ (May 2013) \emph{Automated Flow Cytometry Data Analysis with the OpenCyto Framework}. Cyto 2013, San Diego, California, USA. (poster)} 
	\resitem{\textbf{Ramey, J. A.} (August 2012). \emph{On the Estimation of Similarity Indices in Clustering Evaluation}. Joint Statistical Meetings, San Diego, California, USA.}
	\resitem{\textbf{Ramey, J. A.} and Young, D. M. (August 2010). \emph{Efficient Model Selection for Regularized Discriminant Analysis}. Joint Statistical Meetings, Vancouver, British Columbia, Canada. (poster)}
	\resitem{\textbf{Ramey, J. A.} (April 2010). \emph{Bayesian Regularized Logistic Regression in High-Dimensional Classification}. Instituto Panamericano de Estudios Avanzados en Probabilidad y Estad\'{i}stica: Semana en M\'{e}todos de Reducci\'{o}n de Dimensi\'{o}n. Centro de Investigaci\'{o}n en Matem\'{a}ticas, A.C. Guanajuato, Mexico. (poster)}
\end{itemize}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\resheading{Journal Reviewer}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{itemize}
	\resitem{Journal of Statistical Computation and Simulation}
	\resitem{Journal of Statistical Software}
\end{itemize}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\resheading{Professional Service}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{itemize}
	\item \ressubheading{Session on Generalized Linear and Mixed Models}{Joint Statistical Meetings}{Chair}{August 2012, San Diego, CA, USA}
\end{itemize}

\clearpage

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\resheading{Teaching Experience}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{itemize}
\item
	\ressubheading{Elementary Statistics}{Baylor University}{Teacher of Record}{Aug. 2009 - May 2011}
	\begin{itemize}
		\resitem{Taught this freshman level course in the Statistics Department.}
		\resitem{Developed homework, quizzes and exams for the class.}
		\resitem{Attended weekly meetings to enhance and improve teaching skills and techniques.}
	\end{itemize}
\item
	\ressubheading{Statistics Department Tutoring Lab}{Baylor University}{Graduate Teaching Assistant}{Aug. 2008 - May 2011}
	\begin{itemize}
		\resitem{Conducted one-on-one and group tutoring to students in undergraduate statistics courses.}
	\end{itemize}
\item
	\ressubheading{Statistics for Psychology Majors}{Baylor University}{Graduate Teaching Assistant}{Aug. 2008 - Jul. 2009}
	\begin{itemize}
		\resitem{Provided weekly supplemental instruction to a small group of undergraduate students.}
		\resitem{Lectured to a large number of students in an auditorium during professor absences.}
		\resitem{Led weekly course seminars.}
	\end{itemize}
\end{itemize}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\resheading{Professional Membership}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{itemize}
	\item
		\ressubheading{American Statistical Association}{}{}{2008-present}
	%\item
	%	\ressubheading{Association for Computing Machinery}{}{}{2011-present}
	%\item
	%	\ressubheading{Institute of Electrical and Electronics Engineers}{}{}{2011-present}
\end{itemize}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\resheading{Skills}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{itemize}
\item
	\ressubheading{Programming and Markup Languages}{}{}{}
	\begin{itemize}
		\resitem{{\bf Skilled:} R}
		\resitem{{\bf Proficient:} \LaTeX, Linux, Python, SQL}
		\resitem{{\bf Experienced:} ASP, BUGS, C\#, C++, Java, Mathematica, MATLAB, .NET, PHP}
	\end{itemize}
\end{itemize}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\resheading{Miscellaneous}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{itemize}
\item
	\ressubheading{Innovation in Graduate Education Challenge}{National Science Foundation}{Judge}{2013} 
\item
	\ressubheading{Systems and Computational Biology Affinity Group}{Fred Hutchinson Cancer Center}{Co-Organizer}{2013}
\item
	\ressubheading{United States Soccer Federation}{}{Referee}{1995 - present}
\end{itemize}

\clearpage

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\resheading{References}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{itemize}
	\item
		\ressubheading{Dr. Dean Young (Ph.D. Adviser)}{}{Department of Statistical Science, Baylor University}{}
		%\item	Dean (underscore) Young (at) baylor (dot) edu
		%\item \url{254.710.6183}
		%\item Contact information available upon request.
	\item
		\ressubheading{Dr. John Seaman}{}{Department of Statistical Science, Baylor University}{}
		%\item	John (underscore) Seaman (at) baylor (dot) edu
	\item
		\ressubheading{Dr. Landon Sego}{}{Applied Statistics and Computational Modeling, Pacific Northwest National Laboratory}{}
		%\item	landon (dot) sego (at) pnnl (dot) gov
		%\item 254.710.6181
		%\item Contact information available upon request.
	\item
		\ressubheading{Dr. James Stamey}{}{Department of Statistical Science, Baylor University}{}
		%\item	James (underscore) Stamey (at) baylor (dot) edu
		%\item \url{254.710.7405}
		%\item Contact information available upon request.
\end{itemize}

\end{document}