% (c) 2002 Matthew Boedicker <mboedick@mboedick.org> (original author) http://mboedick.org
% (c) 2003-2007 David J. Grant <davidgrant-at-gmail.com> http://www.davidgrant.ca
% (c) 2008 Nathaniel Johnston <nathaniel@nathanieljohnston.com> http://www.nathanieljohnston.com
%
%This work is licensed under the Creative Commons Attribution-Noncommercial-Share Alike 2.5 License. To view a copy of this license, visit http://creativecommons.org/licenses/by-nc-sa/2.5/ or send a letter to Creative Commons, 543 Howard Street, 5th Floor, San Francisco, California, 94105, USA.

\documentclass[letterpaper,11pt]{article}
\newlength{\outerbordwidth}
\pagestyle{empty}
\raggedbottom
\raggedright
\usepackage[svgnames]{xcolor}
\usepackage{framed}
\usepackage{tocloft}


%-----------------------------------------------------------
%Edit these values as you see fit

\setlength{\outerbordwidth}{3pt}  % Width of border outside of title bars
\definecolor{shadecolor}{gray}{0.75}  % Outer background color of title bars (0 = black, 1 = white)
\definecolor{shadecolorB}{gray}{0.93}  % Inner background color of title bars


%-----------------------------------------------------------
%Margin setup

\setlength{\evensidemargin}{-0.25in}
\setlength{\headheight}{0in}
\setlength{\headsep}{0in}
\setlength{\oddsidemargin}{-0.25in}
\setlength{\paperheight}{11in}
\setlength{\paperwidth}{8.5in}
\setlength{\tabcolsep}{0in}
\setlength{\textheight}{9.5in}
\setlength{\textwidth}{7in}
\setlength{\topmargin}{-0.3in}
\setlength{\topskip}{0in}
\setlength{\voffset}{0.1in}


%-----------------------------------------------------------
%Custom commands
\newcommand{\resitem}[1]{\item #1 \vspace{-2pt}}
\newcommand{\resheading}[1]{\vspace{8pt}
  \parbox{\textwidth}{\setlength{\FrameSep}{\outerbordwidth}
    \begin{shaded}
\setlength{\fboxsep}{0pt}\framebox[\textwidth][l]{\setlength{\fboxsep}{4pt}\fcolorbox{shadecolorB}{shadecolorB}{\textbf{\sffamily{\mbox{~}\makebox[6.762in][l]{\large #1} \vphantom{p\^{E}}}}}}
    \end{shaded}
  }\vspace{-5pt}
}
\newcommand{\ressubheading}[4]{
\begin{tabular*}{6.5in}{l@{\cftdotfill{\cftsecdotsep}\extracolsep{\fill}}r}
		\textbf{#1} & #2 \\
		\textit{#3} & \textit{#4} \\
\end{tabular*}\vspace{-6pt}}
%-----------------------------------------------------------

% Remove the bullet points.
\renewcommand{\labelitemi}{}

\begin{document}

\begin{tabular*}{7in}{l@{\extracolsep{\fill}}r}
\textbf{\Large John A. Ramey II} &  \\
Ph.D. Candidate, Department of Statistics, Baylor University & johnramey@gmail.com \\
Waco, Texas, USA & http://johnramey.net \\
\end{tabular*}
\\

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\resheading{Personal Statement}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
  \begin{center}
  \parbox{6.762in}{My research interests are primarily in applied statistics in the areas of statistical pattern recognition, machine learning, high-dimensional multivariate analysis, and computational statistics.}
  \end{center}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\resheading{Education}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{itemize}
\item
	\ressubheading{Baylor University}{Waco, TX}{Ph.D. Statistics}{May 2012 (Anticipated)}
	\begin{itemize}
		\resitem{Advisor: Dean M. Young, Ph.D.}
		%\resitem{Dissertation: To Be Determined}
	\end{itemize}
\item
	\ressubheading{Baylor University}{Waco, TX}{M.Sc. Statistics}{Dec. 2009}
\item
	\ressubheading{Baylor University}{Waco, TX}{B.Sc. Mathematics (Minor: Computer Science)}{Aug. 2008}
\end{itemize}
  
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\resheading{Awards, Grants \& Honors}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
	\vspace{-2pt}
	\begin{center}\begin{tabular*}{6.6in}{l@{\extracolsep{\fill}}r}
		\multicolumn{2}{c}{Outstanding Graduate Student - Department of Statistical Science\cftdotfill{\cftdotsep}2011}\\
		\multicolumn{2}{c}{JSM Stat Bowl - Champion\cftdotfill{\cftdotsep} 2010}\\
		\multicolumn{2}{c}{Outstanding First Year Graduate Student - Department of Statistical Science\cftdotfill{\cftdotsep}2009}\\
		\multicolumn{2}{c}{Baylor University Dean's Scholarship \cftdotfill{\cftdotsep} 2008-2013}\\
		\vphantom{E}
\end{tabular*}
\end{center}\vspace*{-16pt}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\resheading{Publications}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{itemize}
	\resitem{Ramey, J. A. and Young, P. D. (2012), ``A Comparison of Regularization Methods Applied to the Linear Discriminant Function with High-Dimensional Microarray Data", \textit{Journal of Statistical Computation and Simulation}. (in press)}
	\resitem{Greer, B., Young, D., Harvill, J., and Ramey, J., \textit{Pseudo-likelihood Intervals for the Ratio of Two Poisson Rates with Data Subject to Under-Reporting}. (submitted)}
\end{itemize}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\resheading{Conference Papers}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{itemize}
	\resitem{Ramey, J. A. and Young D. M. (2010). \textit{A More Computationally Efficient Model Selection Method for Regularized Discriminant Analysis}, Joint Statistical Meetings Proceedings, Vancouver, BC, Canada.}
\end{itemize}

\clearpage

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\resheading{Presentations}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{itemize}
	\resitem{Ramey, J. A. (February 2011) \emph{Diagonal Discriminant Analysis after Simultaneous Diagonalization of Covariance Matrices with High-Dimensional Data}. Pacific Northwest National Laboratory, Richland, Washington, USA.}
	\resitem{Ramey, J. A. and Young, D. M. (August 2010) \emph{Efficient Model Selection for Regularized Discriminant Analysis}. Joint Statistical Meetings, Vancouver, British Columbia, Canada.}
	\resitem{Ramey, J. A. (April 2010) \emph{Bayesian Regularized Logistic Regression in High-Dimensional Classification}. Instituto Panamericano de Estudios Avanzados en Probabilidad y Estad\'{i}stica: Semana en M\'{e}todos de Reducci\'{o}n de Dimensi\'{o}n. Centro de Investigaci\'{o}n en Matem\'{a}ticas, A.C. Guanajuato, Mexico.}
\end{itemize}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\resheading{Working Papers}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{itemize}
	\resitem{Ramey, J. A., Young, P. D., and Young D. M., \textit{Improvements to Diagonal Linear Discriminant Analysis with High Dimensional Microarray Data}.}
	\resitem{Ramey, J. A., Young, P. D., and Young D. M., \textit{On Applying Diagonalization to Covariance Matrices for Diagonal Quadratic Discriminant Analysis via Generalized EIgenvalues: Improved Supervised Classification with High Dimensional Microarray Data}.}
	\resitem{Ramey, J. A., Young, P. D., and Young D. M., \textit{Regularized Diagonal Discriminant Analysis with Simultaneous Diagonalization of Covariance Matrices}.}
	\resitem{Ramey, J. A., Young, P. D., and Young D. M., \textit{A More Computationally Efficient Model Selection Method for Regularized Discriminant Analysis}.}
	\resitem{Ramey, J. A., Young, P. D., and Young D. M., \textit{Model Selection for Regularized Discriminant Analysis with Distance Measures}.}
	\resitem{Ramey, J. A., Young, P. D., and Young D. M., \textit{Improving Classification Rates of Regularized Discriminant Analysis: Model Selection with Nonparametric Regression}.}
	\resitem{D.M. Young, Ramey, J. A., and Young, P. D., \textit{A Note on Nonnegative-definite Covariance Structures for which the BLU, WLS, and LS Estimators Are Equal}. (submitted)}
	\resitem{Young, P. D., Ramey, J. A., and Young D. M., \textit{A Matrix Skew Normal Distribution}.}
	\resitem{Ramey, J. A., Young, P. D., and Young D. M., \textit{On the Performance of High-Dimensional Classifiers after Transforming Features to Multivariate Normality}.}
	\resitem{Ramey, J. A., Young, P. D., and Young D. M., \textit{Regularized Discriminant Analysis: A Modern Approach to Model Selection  with High Performance Computing in {\tt R} with the {\tt regdiscrim} Package}.}
	\resitem{Ramey, J. A., Young, P. D., and Young D. M., \textit{Bayesian Regularized Logistic Regression in High-Dimensional Classification}.}
\end{itemize}

\clearpage

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\resheading{Other Research Experience}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{itemize}
	\item
		\ressubheading{Statistical and Machine Learning Research Group}{Waco, TX}{Department of Statistical Science, Baylor University}{2009-present}
	\item
		\ressubheading{Research Experience for Undergraduates at The Ohio State University}{Columbus, OH}{Vertical Integration of Research and Education in Computational Mathematics}{Summer 2004}
	\begin{itemize}
		\resitem{Focused on Number Theory, especially Random Matrix Theory.}
	\end{itemize}
\end{itemize}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\resheading{Professional Membership}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{itemize}
	\item
		\ressubheading{Founder -- R Users Group}{Waco, TX}{Department of Statistical Science, Baylor University}{2010-present}
	\item
		\ressubheading{Member -- American Statistical Association}{}{}{2008-present}
\end{itemize}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\resheading{Teaching Experience}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{itemize}
\item
	\ressubheading{Elementary Statistics}{Baylor University}{Teacher of Record}{Aug. 2009 - Present}
	\begin{itemize}
		\resitem{Taught this freshman level course in the Statistics Department.}
		\resitem{Developed homework, quizzes and exams for the class.}
		\resitem{Attended weekly meetings to enhance and improve teaching skills and techniques.}
	\end{itemize}
\item
	\ressubheading{Statistics Department Tutoring Lab}{Baylor University}{Graduate Teaching Assistant}{Aug. 2008 - Present}
	\begin{itemize}
		\resitem{Provided one-on-one and group tutoring to students in undergraduate statistics courses.}
	\end{itemize}
\item
	\ressubheading{Statistics for Psychology Majors}{Baylor University}{Graduate Teaching Assistant}{Aug. 2008 - Jul. 2009}
	\begin{itemize}
		\resitem{Supplemental Instruction.}
		\resitem{Led weekly course seminars.}
	\end{itemize}
\end{itemize}

\clearpage

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\resheading{Work Experience}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{itemize}
\item 
	\ressubheading{Pacific Northwest National Laboratory}{Richland, WA}{Research Associate}{June 2011 - Present}
%	\begin{itemize}
%		\resitem{Initiated development of a new flagship product using the .NET platform.}
%	\end{itemize}

\item 
	\ressubheading{Candidate Resources, Inc.}{Grand Prairie, TX}{Senior Web Programmer}{Jan. 2007 - Nov. 2007}
	\begin{itemize}
		\resitem{Initiated development of a new flagship product using the .NET platform.}
		\resitem{Maintained a legacy code base written in Classic ASP.}
		\resitem{Administrated MS SQL Server and MS Access databases for clients.}
		\resitem{Provided technical support to staff and clients.}
	\end{itemize}

\item
	\ressubheading{Baylor University, Electronic Libraries}{Waco, TX}{Student Programmer}{Aug. 2006 - Dec. 2006, Aug. 2007 - May 2008}
	\begin{itemize}
		\resitem{Developed PHP websites and scripts with Oracle databases for Baylor faculty and staff.}
	\end{itemize}
	\ressubheading{}{}{Instructional Technology Assistant}{Feb. 2002 - Aug. 2006}
	\begin{itemize}
		\resitem{Instructed Baylor faculty and staff one-on-one and in seminars on Microsoft Office and educational software.}
	\end{itemize}
\end{itemize}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\resheading{Skills}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{itemize}
\item
	Programming and Markup Languages
	\begin{itemize}
		\resitem{{\bf Skilled:} R}
		\resitem{{\bf Proficient:} ASP.NET, Classic ASP, C\#, \LaTeX, PHP, SQL, WinBUGS}
		\resitem{{\bf Currently Learning:} Python}
	\end{itemize}

\item
	Specialized Software
	\begin{itemize}
		\resitem{JMP, Mathematica, MATLAB,  Microsoft Office, Microsoft SQL Server, Microsoft Visual Studio, Oracle, SAS}
	\end{itemize}
\end{itemize}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\resheading{References}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{itemize}
	\item
		\ressubheading{Dr. Dean Young (Adviser)}{}{Department of Statistical Science, Baylor University}{}
	%\item	Dean\_Young@baylor.edu
	%\item 254.710.6183
	\item Contact information available upon request.
	\item
		\ressubheading{Dr. John Seaman}{}{Department of Statistical Science, Baylor University}{}
	%\item	John\_Seaman@baylor.edu
	%\item 254.710.6181
	\item Contact information available upon request.
	\item
		\ressubheading{Dr. James Stamey}{}{Department of Statistical Science, Baylor University}{}
	%\item	James\_Stamey@baylor.edu
	%\item 254.710.7405
	\item Contact information available upon request.
\end{itemize}

\end{document}